SETI in the Optical Spatial-Temporal Domain

### 2019-04-16 paper/ms.tex
start writing section 3

In this paper I explore the potential for wide-field time domain surveys in conducting a new generation of technosignature searches. 
In \S\ref{sec:method} I describe the general principles behind technosignature searches in time domain surveys, including spatial over-densities of light curve signals and coordinated signals between multiple sources, for example.
In \S\ref{sec:haystack} I introduce several relevant surveys, and use the ``Cosmic Haystack'' search volume metric developed by \citet{wright2018c} to quantitatively compare these surveys to current radio SETI approaches. 
The data-driven spatial-temporal domain explored by these surveys necessitates new SETI approaches be developed, and in \S\ref{sec:transit} I outline an example signal where transiting planets around many stars could act as a spatially distributed beacon network.
Finally in \S\ref{sec:discussion} I discuss ideas for other search approaches, and the advantages in cost and reproducibility of conducting SETI with current and upcoming optical time domain surveys.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Potential Strategies}

@@

\citep{lacki2019} looking for specular reflections of interplanetary objects, particularly in big new surveys

several kinds of signals have been suggested that may be viable. Here I list a few general classes of technosignature signals that may be well suited for developing detection algorithms around:

\begin{itemize}
\item unusual variability -- either on short timescales (e.g. Boyajian's Star) or long timescales (e.g. VASCO)
\item spatial correlations of events or phenomena -- e.g. coordination of transiting systems, or rebroadcasting events such as novae along the ``SETI ellipse'' \citep{makovetskii1977,lemarchand1994,tarter2001,shostak2004}
\item spatial density or distribution -- e.g. an over density of phenomena, such as within the Earth Transit Zone \citep{heller2016}
\item unnatural patterns, particularly of otherwise normal variability -- e.g. a prime or fibonacci sequence
\end{itemize}

>>>>

In this paper I explore the potential for wide-field time domain surveys in conducting a new generation of technosignature searches, starting with an overview of the motivation for doing SETI with optical surveys in \S\ref{sec:method}.
In \S\ref{sec:strategy} I describe the general principles behind technosignature searches in time domain surveys, including spatial over-densities of light curve signals and coordinated signals between multiple sources, for example.
In \S\ref{sec:haystack} I introduce several relevant surveys, and use the ``Cosmic Haystack'' search volume metric developed by \citet{wright2018c} to quantitatively compare these surveys to current radio SETI approaches. 
The data-driven spatial-temporal domain explored by these surveys necessitates new SETI approaches be developed, and in \S\ref{sec:transit} I outline an example signal where transiting planets around many stars could act as a spatially distributed beacon network.
Finally in \S\ref{sec:discussion} I discuss ideas for other search approaches, and the advantages in cost and reproducibility of conducting SETI with current and upcoming optical time domain surveys.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Potential Strategies}
\label{sec:strategy}

@@

Several types of signals have been suggested that may be viable for use with optical surveys. For example, \citet{villarroel2016} searched two wide field, single-epoch optical surveys for objects ``disappearing''  over decades timescales. \citet{lacki2019} outline a method to search for specular reflections of interplanetary objects, particularly in wide field surveys. \citet{arnold2005} describe the the observable signature of transits from ostensibly artificial objects, which could be searched for with exoplanet transit surveys.

Here I list a few general classes of technosignature signals that may be well suited for developing new detection algorithms around:

\begin{itemize}
\item unusual variability profiles or statistical distributions -- either on short timescales (e.g. Boyajian's Star) or long timescales (e.g. VASCO)
\item spatial correlations of events or phenomena -- e.g. coordination of transiting systems, or rebroadcasting events such as novae along the ``SETI ellipse'' \citep{makovetskii1977,lemarchand1994,tarter2001,shostak2004}
\item spatial density or distribution -- e.g. an over density of phenomena, such as within the Earth Transit Zone \citep{heller2016}
\item unnatural patterns, particularly patterns of otherwise normal variability -- e.g. a prime or fibonacci sequence
\end{itemize}
